Magnetized accretion disks around Kerr black holes with scalar hair - I. Constant angular momentum

### 2018-06-07 paper_prd.tex
typo corrected

We consider a constant angular momentum distribution $l(r,\theta) = \mathrm{cte}.$. The specific value of the angular momentum is computed as the minimum of the following equation
\begin{equation}\label{eq:mb_ang_mom}
l^{\pm}_{\mathrm{b}}(r, \theta) = \frac{g_{t\phi}\pm\left(\sqrt{g_{t\phi}^2-g_{tt}g_{t\phi}}\right)\sqrt{1+g_{tt}}}{-g_{tt}}
\end{equation}
where the plus sign is for prograde orbits and the minus is for retrograde orbits.
This expression is given by~\citep{Daigne:2004} for Kerr BHs, but it is valid for any stationary, axisymmetric spacetimes. For prograde motion, the function has a minimum outside the event horizon. The location of said minimum corresponds with the marginally bound orbit $r_{\mathrm{mb}}$, and the angular momentum corresponds to the keplerian angular momentum $l_{\mathrm{mb}}$ at that point. We show the proof of this statement at appendix~\ref{ang_mom_appendix}. This choice of angular momentum distribution is motivated by its simplicity (for a first study of thick tori around KBHsSH) and for allowing the presence of a cusp (to allow matter accretion onto the black hole) and a centre.

>>>>

We consider a constant angular momentum distribution $l(r,\theta) = \mathrm{cte}.$. The specific value of the angular momentum is computed as the minimum of the following equation
\begin{equation}\label{eq:mb_ang_mom}
l^{\pm}_{\mathrm{b}}(r, \theta) = \frac{g_{t\phi}\pm\left(\sqrt{g_{t\phi}^2-g_{tt}g_{\phi\phi}}\right)\sqrt{1+g_{tt}}}{-g_{tt}}
\end{equation}
where the plus sign is for prograde orbits and the minus is for retrograde orbits.
This expression is given by~\citep{Daigne:2004} for Kerr BHs, but it is valid for any stationary, axisymmetric spacetimes. For prograde motion, the function has a minimum outside the event horizon. The location of said minimum corresponds with the marginally bound orbit $r_{\mathrm{mb}}$, and the angular momentum corresponds to the keplerian angular momentum $l_{\mathrm{mb}}$ at that point. We show the proof of this statement at appendix~\ref{ang_mom_appendix}. This choice of angular momentum distribution is motivated by its simplicity (for a first study of thick tori around KBHsSH) and for allowing the presence of a cusp (to allow matter accretion onto the black hole) and a centre.
